### 2021-02-17 rad-icfp-2021/macrodiff.tex
some comments
some more basic writing

>>>>

\subsubsection{Reverse AD for unary operators}

We define reverse-mode by the following inductively defined macro $\Dsynrevsymbol[\rho]:\TSSyn\to \TTSynHO$, where $\rho$ is some type of our language, on both types and terms.

\[
\begin{array}{l}
\Dsynrev[\rho]{A} \defeq A\times (A\To \rho)
\end{array}    
\]

\[
\begin{array}{l}
	 \Dsynrev[\rho]{var_{i,\Gamma}}:= \var,Y\vdash \tPair{var_{i,\Gamma}}{\lambda \var[2]. Y(Jvar_{i,\Gamma}^T(\var[2]))}\\
	 \Dsynrev[\rho]{\op_{n,\Gamma}}:= \var,Y\vdash \tPair{\op_{n,\Gamma}}{\lambda \var. Y(J\op_{n,\Gamma}^T(\var))}\\
	 \Dsynrev[\rho]{\trm;\trm[2]}:= \var,Y\vdash \Dsynrev[\rho]{\trm[2]}(\Dsynrev[\rho]{\trm}(\var,Y))\\
	 \Dsynrev[\rho]{swap_\sigma}:= \var,Y\vdash \tPair{swap_\sigma}{\lambda \var[2].Y(Jswap_\sigma^T(\var[2]))} \\
	 \Dsynrev[\rho]{b:\BB\text{ or }\NN}:= \var,Y\vdash \tPair{b}{\lambda \var[2].Y(\underline{0})}\\
	 \Dsynrev[\rho]{\widehat{\trm}}:= \var,Y\vdash \tMatch{\Dsynrev[\rho]{\trm}}{\var[2],Y'}{\tPair{\widehat{\trm}}{\lambda \var[2].\tMatch{\var[2]}{\var[2]_1,\var[2]_2}{Y'(\var[2]_1)}}}\\
	 \Dsynrev[\rho]{\ifelse{\trm}{\trm_1}{\trm_2}}:=\var,Y\vdash\ifelse{\trm}{\Dsynrev[\rho]{\trm_1}}{\Dsynrev[\rho]{\trm_2}}\\
\end{array}
\]

Observe that we use the transposed matrix of partial derivatives in the differentiation of an operation.
Moreover, observe that we accumulate such transposed derivatives in reverse order, by making use of continuation passing style.
